Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: more tweaks

\subsection{Implementation}
To evaluate the performance of our approach, we implement a prototype system in Java, following a traditional iterator model.
Our database handles a subset of standard SQL queries, including filters, joins, projection, grouping and aggregation.
For simplicity, \ProjectName{} only handles tables containing integer data.

@@

%\begin{figure}
%\includegraphics[width=\columnwidth]{figures/planning_times_imputedb.png}
%\caption{Planning times for each query}
%\label{fig:plantimes}
%\end{figure}
\vspace{0.5in}
\subsubsection{Accuracy vs. Base-table Imputation}

>>>>

\subsection{Implementation}
To evaluate the performance of our approach, we implemented a prototype system in Java, following a traditional iterator model.
Our database handles a subset of standard SQL queries, including filters, joins, projection, grouping and aggregation.
For simplicity, \ProjectName{} only handles tables containing integer data.

@@

%\begin{figure}
%\includegraphics[width=\columnwidth]{figures/planning_times_imputedb.png}
%\caption{Planning times for each query}
%\label{fig:plantimes}
%\end{figure}
\subsubsection{Accuracy vs. Base-table Imputation}
